---
title: "My Shiny App"
author: "Gautam"
date: "4 February 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App overview

The application takes `name`, `date of birth`, `height (cm)` and `weight (kg)` of the user as input. It returns the user's `age`, the `weekday` of their birth and their `BMI`.  

It also displays a BMI chart against which the user can check their BMI to see if they are in the normal range.  

## App and Code

Click [here](https://gautamp7.shinyapps.io/MyShinyApp/) to acces the Shiny web application deployed on shinyapps.io  

Click [here](https://github.com/GautamP7/ShinyApp-Coursera) to access the Github repo containing the source code for the web application  

## Sample output of the app

```{r, message=FALSE, echo=TRUE, results='hide'}
library(lubridate)
dob <- as.Date("1989-01-01"); height <- 180; weight <- 72
age <- as.period(interval(start = dob, end = Sys.Date()))$year
day <- weekdays(dob)
bmi <- weight / ((height / 100) ^ 2)
print("Hi John")
print(paste("Your age is ", age))
print(paste("You were born on ", day))
print(paste("Your BMI is ", bmi))
```

```{r, message=FALSE}
library(lubridate)
dob <- as.Date("1989-01-01")
height <- 180
weight <- 72
age <- as.period(interval(start = dob, end = Sys.Date()))$year
day <- weekdays(dob)
bmi <- weight / ((height / 100) ^ 2)
print("Hi John")
print(paste("Your age is ", age))
print(paste("You were born on ", day))
print(paste("Your BMI is ", bmi))
```

## THE END